% !TeX program = pdflatex
\documentclass[11pt,a4paper]{article}

% Essential packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{float}
\usepackage{cleveref}
\usepackage{titling}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning}

% Page layout
\geometry{
    a4paper,
    margin=2.5cm
}

% Hyperref settings
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    citecolor=blue
}

% Document info
\title{Songjam\\[0.5em]\large A Cryptographic Voice Verification System}
\author{Adam Place}
\date{\today}

% Customize title formatting
\pretitle{\begin{center}\LARGE\bfseries}
\posttitle{\par\end{center}}

\begin{document}

\maketitle

\begin{abstract}
A fully encrypted, privacy-preserving voice verification system could effectively eliminate voice-based deepfake fraud without requiring users to compromise their security or personal data.
Zero-knowledge proofs provide part of the solution, but a fundamental challenge remains: it is difficult to verify with absolute certainty that a given voice truly belongs to a specific individual, especially as voice synthesis technologies become increasingly sophisticated.
This work introduces a solution to the verification problem by leveraging cryptoeconomics.
The network rewards users for submitting accurate credentials, while imposing penalties on those who attempt to provide false information, leveraging the security of a Proof-of-Stake (PoS) consensus mechanism, while aligning user incentives with the integrity of the network.
Voice biometrics and other sensitive data are cryptographically stored in Trusted Execution Environments (TEEs) providing hardware-backed isolation and encryption.
Access to this data is granted to users through a Soulbound Token (SBT), a non-transferable, non-replicable digital asset permanently tied to an individual’s digital identity.
Over time, the user builds-up a personalised voice model, with each new audio sample organized and stored within a wavRAG structure—an Audio-Integrated Retrieval Augmented Generation framework, enabling efficient and context-rich retrieval of voice data.
\end{abstract}

\section{Introduction}
\label{sec:introduction}
The rise of deepfakes has led to a growing concern about the falibility of humans to verify the authenticity of voice communication.
High profile cases such as the 2024 deepfake attack on engineering firm Arup, which led to a twenty-five million dollar loss, highlight the importance of secure and reliable enterprise verification systems.

While a plethora of fradulent online videos featuring deepfakes of celebrities promoting supposed investment opportunities, and the rise of romance or 'pig butchering' scams which collectively siphon billions of dollars from unsuspecting victims every year illustrate the nessecity of consumer or citizen protections.
The sub-150ms latency required for natural conversation in VoIP calls leaves minimal time for analysis on standard hardware, making real-time detection of deepfakes challenging. While the proprietary nature of platforms such as Zoom, Teams and SIP providers, hinders the development of universal detection frameworks.

What is needed is a privacy-preserving verification system leveraging zero-knowledge proofs and selective disclosure mechanisms, where only cryptographically attested credentials (e.g., identity, access rights) are validated—without exposing extraneous user data.
This approach ensures networks authenticate voice participants a priori through mathematical guarantees (e.g., zk-SNARKs), verifying the existence of valid credentials rather than analyzing raw biometrics or personal details.
By limiting verification to key attributes (e.g., "member of authorised group" or "registered device") and eliminating unnecessary data collection, such systems align with GDPR/CCPA principles while thwarting deepfake fraud and metadata misuse.
This paper proposes a novel cryptoeconomic framework for voice verification, in which users are incentivised to provide accurate and verifiable credentials, while malicious actors face penalties—akin to Proof-of-Stake (PoS) slashing mechanisms—for fraudulent voice attribution attempts.

\section{The Proof-of-Stake Security Guarentee?}
\label{sec:background}
Much has been written about the security of the PoS consensus mechanism, with proponents arguing that its economic incentives guarantee security, while opponents contend that the consolidation of staked token supply will lead to centralisation.
Nevertheless, the economic incentives and penalties underpinning Ethereum’s Proof-of-Stake mechanism have proven effective, driving its adoption and establishing it as the preferred consensus model for securing one of the world’s largest blockchain networks—demonstrated by the very small number of validator slashing events recorded to date (with only around 0.045\% of validators slashed since Ethereum staking began).

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[
        node distance=2.8cm,
        block/.style={rectangle, draw, text width=2.2cm, text centered, minimum height=0.8cm},
        validator/.style={circle, draw, text width=1.8cm, text centered, minimum height=0.8cm},
        arrow/.style={thick,->,>=stealth},
        dashedarrow/.style={thick,dashed,->,>=stealth},
        math/.style={rectangle, draw, text width=2.8cm, text centered, minimum height=1.2cm},
        reward/.style={rectangle, draw, text width=2.2cm, text centered, minimum height=0.8cm, fill=green!20}
    ]
        % Blockchain
        \node[block] (blockchain) {Blockchain};
        
        % Validators - using larger distances
        \node[validator, left=2.8cm of blockchain] (validator1) {Compliant};
        \node[validator, right=2.8cm of blockchain] (validator2) {Non-Compliant};
        
        % Staking connections
        \draw[dashedarrow] (validator1) -- node[above] {32 ETH} (blockchain);
        \draw[dashedarrow] (validator2) -- node[above] {32 ETH} (blockchain);
        
        % Slashing penalty
        \node[math, below=of blockchain] (penalties) {
            Slashing = $\frac{32}{32} \times \text{min}(S, 32)$\\
            $S$ = effective balance
        };
        
        % Stake reduction
        \node[block, right=of penalties] (reduction) {Stake -16 ETH};
        
        % Rewards
        \node[reward, below=of validator1] (rewards) {
            Rewards = $\frac{\text{Base} \times \text{Eff}}{32}$
        };
        
        % Connections
        \draw[arrow] (blockchain) -- node[right] {Non-Compliant} (penalties);
        \draw[arrow] (penalties) -- node[above] {Calc} (reduction);
        \draw[arrow] (reduction) to[bend right=35] node[right, yshift=0.2cm] {Slash} (validator2);
        \draw[arrow] (blockchain) -- node[left] {Compliant} (rewards);
        \draw[arrow] (rewards) to[bend left=35] node[left, yshift=0.2cm] {Reward} (validator1);
    \end{tikzpicture}
    \caption{Ethereum's PoS economics rewards honest validators and penalises malicious ones}
    \label{fig:pos-system}
\end{figure}



\section{Soulbound Tokens}
\label{sec:methodology}
Describe your methods and approach here.

\section{Voice Biometrics}
\label{sec:results}
Present your results here.

\section{AI Voice Agents}
\label{sec:discussion}
Discuss your findings and their implications here.

\section{Conclusion}
\label{sec:conclusion}
Conclude your paper here.

\bibliographystyle{plain}
\bibliography{references}

\end{document} 